An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
Adding Lemma X

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

>>>>

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\LV}{\mathcal{LV}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\jessie{Lemma X}
\begin{lemma}
	Let $\risk L: \simplex \to \reals$ be a (concave) polyhedral function.
	There exists a unique set of loss vectors $\LV$ of minimum cardinality such that $\risk L(p) = \min_{v \in \LV} \inprod{v}{p}$.
	Define $\Theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$.
	Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
	\begin{enumerate}
		\item $\{L(r^*) \mid r^* \in \R^*\} = \LV$,
		\item $\R^*$ is a minimum representative set for $L$,
		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$,
		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
	\end{enumerate}
\end{lemma}
\begin{proof}
	Since $\risk L$ is a concave polyhedral function, it is the pointwise min of a finite set of linear functions \jessie{Rockafellar}.
	Since $\risk L$ is generated by a finite set of linear functions, the set of linear functions of minimum cardinality is well-defined.
	(1)
\end{proof}
